---
title: "Toolik Chlorophyll Concentrations"
author: "Halina Do-Linh"
date: "8/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(skimr)
```

## Read in toolik_chlorophyll.csv as a data frame stored as "toolik_chlorophyll

```{r}
toolik_chlorophyll <- read_csv(here::here("data", "data-raw", "toolik_chlorophyll.csv"), na = ".")


```

## Explore the imported data with `skimr::skim()`
```{r}
dim(toolik_chlorophyll)
head(toolik_chlorophyll)
tail(toolik_chlorophyll)
skim(toolik_chlorophyll)
names(toolik_chlorophyll)
# I see from names that these column names would be hard to work with because of the capitalization and the spaces

```

## Replace toolik_chlorphyll with toolik_chlorophyll so that the name is right...then replace and use the janitor function
```{r}

toolik_chlorophyll <- toolik_chlorophyll %>% clean_names()

```


## Create a scatterplot of depth versus chlorophyll A concentration

- Make point size `size` changed based on the concentration
- Make all points "cyan"
- Update the theme to `theme_dark()`

```{r}

chlorophyll_plot <- ggplot(data = toolik_chlorophyll, 
                           aes(x = active_chl_a_ug_l, y = depth)) +
  geom_point(aes(size = active_chl_a_ug_l), 
             color = "cyan") +
  theme_dark() +
  scale_y_reverse()

chlorophyll_plot

```

```{r}
ggsave(here::here("figs", "chlorophyll_graph.jpg"), plot = chlorophyll_plot)

```

